---
title: "A View into CRAN TaskView"
author: "Bruce Campbell"
date: "4/8/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidygraph)
library(ggraph)
library(tools)
#install.packages('ggraph')
#install.packages('ctv')
#install.packages('cranlogs')
library(ggraph)
library(ctv)
library(cranlogs)
library(ggthemes)
```

## A view into package connectivity for Spatial modeling in R 

The ctv package gives us access to the Cran Task View repository. The package provides infrastructure for task views to CRAN-style repositories: Querying task views and installing the associated packages (client-side tools), generating HTML pages and storing task view information in the repository.

Let's load up the data for the tidyverse and visualize it.  Then we'll look at the Machine Learnine,Spatial, and SpatioTemporal Task Views. 

```{r,echo=FALSE}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)

all_cran_packages <- tools::CRAN_package_db()[,c("Package", "Imports")] 
tidied_cran_imports <- as_tibble(all_cran_packages) %>% 
  separate_rows(Imports, sep = ",") %>% 
  mutate(Imports = str_replace(Imports,"\\s*\\([^\\)]+\\)","")) %>%
  mutate(Imports = str_trim(Imports, side = "both"))

tidyverse_tbl <- tidied_cran_imports %>% 
  filter(Package %in% tidyverse_packages()) %>%
  filter(Imports %in% tidyverse_packages()) %>%
  as_tbl_graph() 

plot_task_table<-function(task_table, titleText)
{
  p<- ggraph(task_table, layout = 'nicely') + 
    geom_edge_link(colour = "grey50") + 
    geom_node_text(aes(label = name),  size = 6) 
  
  p<-p + theme_solarized() + scale_colour_solarized("blue")
  
  p <- p +  theme(
      plot.background = element_blank()
     ,panel.grid.major = element_blank()
     ,panel.grid.minor = element_blank()
     ,panel.border = element_blank()
    ) 
  p <- p+ theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank()) + 
      theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank())
  p<- p + ggtitle(titleText)
  return(p)
}

plot_task_table(tidyverse_tbl, "tidyverse")
```

```{r,echo=FALSE}

ml_packages <- ctv:::.get_pkgs_from_ctv_or_repos(views = "MachineLearning") %>% 
  unlist(use.names = FALSE)

ml_tbl <- tidied_cran_imports %>%
  filter(Package %in% ml_packages) %>%
  filter(Imports %in% ml_packages) %>%
  as_tbl_graph()

plot_task_table(ml_tbl, "machine learning")
```

```{r,echo=FALSE,fig.width=8,fig.height=10}
sptemp_packages <- ctv:::.get_pkgs_from_ctv_or_repos(views = "Spatial") %>% 
  unlist(use.names = FALSE)

sptem_tbl <- tidied_cran_imports %>%
  filter(Package %in% sptemp_packages) %>%
  filter(Imports %in% sptemp_packages) %>%
  as_tbl_graph()


plot_task_table(sptem_tbl,"spatial")
```


```{r,echo=FALSE}
sptemp_packages <- ctv:::.get_pkgs_from_ctv_or_repos(views = "SpatioTemporal") %>% 
  unlist(use.names = FALSE)

sptem_tbl <- tidied_cran_imports %>%
  filter(Package %in% sptemp_packages) %>%
  filter(Imports %in% sptemp_packages) %>%
  as_tbl_graph()


plot_task_table(sptem_tbl,"spatiotemporal")
```

